---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# dutchparl

<!-- badges: start -->
<!-- badges: end -->

dutchparl - An R package for the Dutch Parliamentary Behaviour Dataset

This package allows users to work easily with the Dutch Parliamentary Behaviour Dataset. There are multiple datasets: one on votes and one on parliamentary (written) questions.


### Installation
To install this package in R:
```r 
install.packages("devtools")
devtools::install_github("louwerse/dutchparl")
``` 

### Download data

The data can be downloaded from Harvard Dataverse: https://dataverse.harvard.edu/dataverse/dutchparl

You can download the voting data in R and save it to a file in your current working directory (default = "votes.rds").
```r
downloadVotes()
```

You can download the questions data in R and save it to a file in your current working directory (default = "questions.rds").
```r
downloadQuestions()
```


### Work with the data
Load the package dutchparl. This includes two example objects `examplevotes` and `examplequestions`, which can be used to demonstrate how the package works. The fulldataset is not included with the package, due to its size (see above for downloading).

```{r}
library("dutchparl")
data = examplevotes
summary(data)
```

You can open the full version of the data using:

```r
votes = loadRDS("votes.rds") # Use name of relevant datafile
```

Available functions can be obtained via:
```r
help(package="dutchparl")
```
